\documentclass{article}
\usepackage{newspaper}
\usepackage{multicol}
\usepackage{textcomp}
\date{\today}
\currentvolume{4}
\currentissue{17}
\begin{document}
\SetPaperName{Northgate Herald}
\SetPaperLocation{Northgate}
\SetPaperSlogan{\it Death to the bourgeois}
\SetPaperPrice{\pounds1.20}
\maketitle
\begin{multicols}{3}
\byline{\sc\bf\LARGE Northgate common has been attacked}{Lorenzo Bercelli}
Fellow Citizens, Northgate common, the pride of our People, the joy of our
children, the park that made us a community in the proper sense of the word, has
been attacked and will probably cease to exist in 3 months time.

"Who has dared to attack us!?  How will they be able to destroy Northgate Common? What is this fool saying, he must be crazy!"
I'm afraid not, startled readers. If you have thought that, you have underestimated, as so often happens, the corruption
and disinterest for the well-being of the community of the fine folks at the Northgate Town Planning Department.

Without any sort of consultation with the locals, despite what they falsely claim, They have planned to transform our dear park
(dismissively referred to as 'unused land'. Unused by their inept, weak, antisocial kind, I say!) into a private housing project, 
destined to God-knows-who and, this is the best part, provided of \textbf{private gardens!} Is Thatcher still ruling this country, even from her grave !?
For how long still will we stand the gratuitous privatization of every common good and public facility, how long yet 'till we will be ready to privatize
the air we breath, the flowers we smell?

To those slaves of the Capital who have already straightened their fingers ready to point at me as a crazy conspiracist, 
I say do not even try to get your mud-machines started, for this time the treacherous intention is terribly clear;
Why else the short notice, the dismissive tone, the lack of information, the invented consultation?
Fellow citizens of Northgate,
Be ready to fight for our park, for the vile and tireless hand of corrupted capitalism is weaving its demise.
\closearticle
\end{multicols}
\end{document}
